---
title: "R Notebook"
output: html_notebook
---


```{r global_options, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning=FALSE, message=FALSE)
```


```{r}
library(readr)
library(readxl)
library(tidyverse)
library(lubridate)
library(janitor)
library(knitr)
library(extrafont)
```

```{r}
# MY THEME
  my_theme <- function() { 
    theme_bw(base_size = 11, base_family = "Roboto Condensed") %+replace% 
      theme(
      plot.title = element_text(color = "black",face = "bold", size = 12),
      plot.subtitle = element_text(color = "black",face = "italic",size = 10),
      axis.text.x = element_text(color = "black",hjust = 0.5),
      axis.text.y = element_text(color = "black",hjust = 1,vjust = 0.4),
      axis.title = element_text(color = "black",size = 9),
     plot.caption = element_text(color = "#AAAAAA",hjust = 1, size = 6)
      )
}
```



```{r}
data <- read_csv("Dataset/allqvdata.csv")
```

```{r}
# to convert variable `Mon-Year Delivered` to date format
data$deliverydate <- dmy(paste("01-", data$`Mon-Year Delivered`,sep = ""))
```


```{r}
library(readr)
sfdata <- read_csv("Dataset/deliveredsep2019.csv")
```



```{r}
sfdata$ActualDeliveryDate <- dmy(sfdata$ActualDeliveryDate)
sfdata$SelectforVerification <- as.numeric(sfdata$SelectforVerification)

```



# SMSU3 (randomly selected by Salesforce from deliveries Mar-Sep 2019) 

```{r}
aa <- sfdata %>% 
  select(ActualDeliveryDate,VerificationOutcome,SelectforVerification) %>% 
  filter(VerificationOutcome != 0,VerificationOutcome != "Pending") %>% 
  mutate(Deliverydate = as.Date(cut(ActualDeliveryDate,breaks = "month"))) %>%
  group_by(VerificationOutcome,Deliverydate)
```

```{r}
aa$VerificationOutcome <- as.factor(aa$VerificationOutcome)
aa$SelectforVerification <- as.numeric(aa$SelectforVerification)
```

```{r}
bb <- aa %>% 
  group_by(VerificationOutcome,Deliverydate) %>% 
  summarize(datacheck = sum(SelectforVerification))
cc <- aggregate(datacheck ~ Deliverydate+VerificationOutcome,data = bb,sum)
dd <- spread(cc, VerificationOutcome, datacheck) 
dd[is.na(dd)] <- 0 # assign NA in the dataframe as zero
dd$Deliverydate <- format(dd$Deliverydate,"%Y %b") # format data to yyyy mmm
ee <- dd %>%   
adorn_totals (c("row","col"))
ee1 <- ee[,c(1,5, 4, 3, 2)] #change column position
```

```{r}
#Change column name
names(ee1)[names(ee1) == "Deliverydate"] <- "Delivery Date"
names(ee1)[names(ee1) == "Total"] <- "Total Verification"
```


```{r}
ee2 <- ee1 %>% 
  mutate(VerifiedFalse_Rate = paste0(format(`Verified False`/(`Verified False`+`Verified True`)*100,digits = 0), "%")) %>% 
  mutate(Unverified_Rate = paste0(format(`Unverified`/(`Unverified`+`Verified False`+`Verified True`)*100,digits = 0), "%"))
# change column names
names(ee2)[names(ee2) == "VerifiedFalse_Rate"] <- "Verified False Rate"
names(ee2)[names(ee2) == "Unverified_Rate"] <- "Unverified Rate"
kable(ee2,caption = " Verification Results",format.args = list(big.mark = ","), align = c("l"))
```

Note:   
*Verified False Rate = Verified False / (Verified False + Verified True)*     
*Unverified Rate = Unverified / (Unverified + Verified False + Verified True)*


# Verification rate by Sales Channel


```{r}
bb <- sfdata %>% 
  group_by(VerificationOutcome,SalesChannel) %>% 
  summarize(datacheck = sum(SelectforVerification))
cc <- aggregate(datacheck ~ SalesChannel+VerificationOutcome,data = bb,sum)
dd <- spread(cc, VerificationOutcome, datacheck) 
dd[is.na(dd)] <- 0 # assign NA in the dataframe as zero
ee <- dd %>%   
adorn_totals (c("row","col"))
ee1 <- ee[,c(1,5, 4, 3, 2)] #change column position
```

```{r}
#Change column name
names(ee1)[names(ee1) == "Deliverydate"] <- "Delivery Date"
names(ee1)[names(ee1) == "Total"] <- "Total Verification"
```


```{r}
ee2 <- ee1 %>% 
  mutate(VerifiedFalse_Rate = paste0(format(`Verified False`/(`Verified False`+`Verified True`)*100,digits = 0), "%")) %>% 
  mutate(Unverified_Rate = paste0(format(`Unverified`/(`Unverified`+`Verified False`+`Verified True`)*100,digits = 0), "%"))
# change column names
names(ee2)[names(ee2) == "VerifiedFalse_Rate"] <- "Verified False Rate"
names(ee2)[names(ee2) == "Unverified_Rate"] <- "Unverified Rate"
names(ee2)[names(ee2) == "SalesChannel"] <- "Sales Channel"
kable(ee2,caption = " Verification Results",format.args = list(big.mark = ","),align = c("l"))
```

Note:   
*Verified False Rate = Verified False / (Verified False + Verified True)*     
*Unverified Rate = Unverified / (Unverified + Verified False + Verified True)*


# Types of mis-reporting

```{r}
enddate_mon <- format(max(sfdata$ActualDeliveryDate),"%b %Y") #end date of smsu2.0
startdate_mon <- format(min(sfdata$ActualDeliveryDate),"%b %Y") #start date of smsu2.0
#set start and end date of smsu for putting at titles of chart
mon_period <- paste0("Types of mis-reporting", " ", "(" , startdate_mon,"-", enddate_mon, ")")
```

```{r}
missreport <- sfdata %>% 
select(VerifiedFalseCategory,
         SalesChannel,SelectforVerification) %>%
  #filter(`ST_LBOdeliveries` != "NA") %>% #filter out NA from 'ST-LBO deliveries'
  filter(VerifiedFalseCategory != "Unverified") %>% 
group_by(VerifiedFalseCategory) %>%
  summarise(Total = sum(SelectforVerification,na.rm = TRUE)) %>% 
mutate(percent = round(Total/sum(Total)*100),label = paste0(Total," ","(",percent,"%",(")")))
totalcases <- paste0("Total cases: ",sum(missreport$Total))
missreport$VerifiedFalseCategory <- reorder(missreport$VerifiedFalseCategory, missreport$Total)
ggplot(missreport,aes(x = VerifiedFalseCategory,y = Total))+ geom_bar(stat = "identity",fill="#42ffe6")+
  theme(text = element_text(family="Roboto Condensed"))+
  geom_text(aes(label=label, hjust = - 0.1,family="Roboto Condensed"),color="black",size=3)+ 
  ggtitle(mon_period,subtitle = totalcases)+ 
  labs(x="", y="Number of mis-reporting")+
  scale_y_continuous(breaks=seq(0,40,10),limit = c(0, 40))+
   coord_flip()+
  my_theme()
```


\newpage

# SMSU3 (randomly selected from deliveries Jul 2018 to Sep 2019)

```{r}
datasmsu3 <- data %>% 
filter(deliverydate >= ymd("2018-06-30"))
```

```{r}
length (datasmsu3$`Mon-Year Delivered`)
```


```{r}
a <- datasmsu3 %>% 
select(`Total selected data`,`Type of cases`,
         `ST_LBOdeliveries`,`Deliveries deleted`) %>%
  filter(`ST_LBOdeliveries` != "NA") %>% #filter out NA from 'ST-LBO deliveries'
group_by(`ST_LBOdeliveries`) %>%
summarise(TotalSelected = sum(`Total selected data`,na.rm = TRUE))
```

```{r}
b <- datasmsu3 %>% 
select(`Total selected data`,`Type of cases`,
         `ST_LBOdeliveries`,`Deliveries deleted`) %>%
   filter(`ST_LBOdeliveries` != "NA") %>% #filter out NA from 'ST-LBO deliveries'
   filter(`Type of cases` != "unverified") %>% 
group_by(`ST_LBOdeliveries`) %>%
  summarise(VerifiedFalse = sum(`Deliveries deleted`,na.rm = TRUE))
```


```{r}
c <- datasmsu3 %>% 
select(`Total selected data`,`Type of cases`,
         `ST_LBOdeliveries`,`Deliveries deleted`) %>%
  filter(`Type of cases` == "unverified") %>% 
   filter(`ST_LBOdeliveries` != "NA") %>% #filter out NA from 'ST-LBO deliveries'
group_by(`ST_LBOdeliveries`) %>%
  summarise(Unverified = sum(`Deliveries deleted`,na.rm = TRUE))
```


```{r, message= FALSE}
d <- right_join(a,b,by = "ST_LBOdeliveries")
```

```{r}
e <- right_join(d,c, by = "ST_LBOdeliveries")
```


```{r}
f <- data.frame(ST_LBOdeliveries = "Total" ,  TotalSelected = sum(e$TotalSelected), VerifiedFalse = sum(e$VerifiedFalse),Unverified = sum(e$Unverified))
```

```{r}
g <- rbind(e,f)
```


```{r}
h <- g %>% 
  mutate(VerifiedTrue = TotalSelected - (VerifiedFalse + Unverified))
i <- h[,c(1,2,5,3,4)] #change column position
```

```{r}
j <- i %>% 
  mutate(VerifiedFalseRate = paste0(format(VerifiedFalse/(VerifiedTrue + VerifiedFalse)*100,digits = 0),"%"),
UnverifiedRate = paste0(format(Unverified/(VerifiedTrue + VerifiedFalse + Unverified)*100,digits = 0), "%"))

```


```{r}
# change column names
names(j)[names(j) == "ST_LBOdeliveries"] <- "SA/LBODeliveries"
names(j)[names(j) == "TotalSelected"] <- "Total Verification"
names(j)[names(j) == "VerifiedTrue"] <- "Verified True"
names(j)[names(j) == "VerifiedFalse"] <- "Verified False"
names(j)[names(j) == "VerifiedFalseRate"] <- "Verified False Rate"
names(j)[names(j) == "UnverifiedRate"] <- "Unverified Rate"
# add total to rows of the table
kable(j,caption = " Verification Results" ,"pandoc",format.args = list(big.mark = ","),align = c("l"))
```

Note:   
*Verified False Rate = Verified False / (Verified False + Verified True)*     
*Unverified Rate = Unverified / (Unverified + Verified False + Verified True)*


# Types of mis-reporting

```{r}
enddate_smsu3 <- format(max(datasmsu3$deliverydate),"%b %Y") #end date of smsu3.0
startdate_smsu3 <- format(min(datasmsu3$deliverydate),"%b %Y") #start date of smsu3.0
#set start and end date of smsu for putting at titles of chart
smsu3_period <- paste0("Types of mis-reporting", " ", "(" , startdate_smsu3,"-", enddate_smsu3, ")")
```

```{r}
missreport <- datasmsu3 %>% 
select(`Type of cases`,
         `ST_LBOdeliveries`,`Deliveries deleted`) %>%
   filter(`ST_LBOdeliveries` != "NA") %>% #filter out NA from 'ST-LBO deliveries'
  filter(`Type of cases` != "unverified") %>% 
group_by(`Type of cases`) %>%
  summarise(Total = sum(`Deliveries deleted`,na.rm = TRUE)) %>% 
mutate(percent = round(Total/sum(Total)*100),label = paste0(Total," ","(",percent,"%",(")")))
totalcases <- paste0("Total cases: ",sum(missreport$Total))
missreport$`Type of cases` <- reorder(missreport$`Type of cases`, missreport$Total)
ggplot(missreport,aes(x = `Type of cases`,y = Total))+ geom_bar(stat = "identity",fill="#42ffe6")+
  theme(text = element_text(family="Roboto Condensed"))+
  geom_text(aes(label=label, hjust = - 0.1,family="Roboto Condensed"),color="black",size=3)+ 
  ggtitle(smsu3_period,subtitle = totalcases)+ 
  labs(x="", y="Number of mis-reporting")+
  scale_y_continuous(breaks=seq(0,60,10),limit = c(0, 60))+
   coord_flip()+
  my_theme()
```

\newpage
# SMSU2.0

```{r}
datasmsu2 <- data %>% 
filter(deliverydate <= ymd("2018-06-30"))
```

```{r}
a <- datasmsu2 %>% 
select(`Total selected data`,`Type of cases`,deliverydate,
         `ST_LBOdeliveries`,`Deliveries deleted`) %>%
  filter(`ST_LBOdeliveries` != "NA") %>% #filter out NA from 'ST-LBO deliveries'
  
group_by(`ST_LBOdeliveries`) %>%
  summarise(TotalSelected = sum(`Total selected data`,na.rm = TRUE))
```

```{r}
b <- datasmsu2 %>% 
select(`Total selected data`,`Type of cases`,
         `ST_LBOdeliveries`,`Deliveries deleted`) %>%
   filter(`ST_LBOdeliveries` != "NA") %>% #filter out NA from 'ST-LBO deliveries'
   filter(`Type of cases` != "unverified") %>% 
group_by(`ST_LBOdeliveries`) %>%
  summarise(VerifiedFalse = sum(`Deliveries deleted`,na.rm = TRUE))
```


```{r}
c <- datasmsu2 %>% 
select(`Total selected data`,`Type of cases`,`Mon-Year Delivered`,
         `ST_LBOdeliveries`,`Deliveries deleted`) %>%
  filter(`Type of cases` == "unverified") %>% 
   filter(`ST_LBOdeliveries` != "NA") %>% #filter out NA from 'ST-LBO deliveries'
group_by(`ST_LBOdeliveries`) %>%
  summarise(Unverified = sum(`Deliveries deleted`,na.rm = TRUE))
```


```{r, message= FALSE}
d <- right_join(a,b,by = "ST_LBOdeliveries")
```

```{r}
e <- right_join(d,c, by = "ST_LBOdeliveries")
```


```{r}
f <- data.frame(ST_LBOdeliveries = "Total" ,  TotalSelected = sum(e$TotalSelected), VerifiedFalse = sum(e$VerifiedFalse),Unverified = sum(e$Unverified))
```

```{r}
g <- rbind(e,f)
```


```{r}
h <- g %>% 
  mutate(VerifiedTrue = TotalSelected - (VerifiedFalse + Unverified))
i <- h[,c(1,2,5,3,4)] #change column position
```

```{r}
j <- i %>% 
  mutate(VerifiedFalseRate = paste0(format(VerifiedFalse/(VerifiedTrue + VerifiedFalse)*100,digits = 0),"%"),
UnverifiedRate = paste0(format(Unverified/(VerifiedTrue + VerifiedFalse + Unverified)*100,digits = 0), "%"))
```


```{r}
# change column names
names(j)[names(j) == "ST_LBOdeliveries"] <- "SA/LBODeliveries"
names(j)[names(j) == "TotalSelected"] <- "Total Verification"
names(j)[names(j) == "VerifiedTrue"] <- "Verified True"
names(j)[names(j) == "VerifiedFalse"] <- "Verified False"
names(j)[names(j) == "VerifiedFalseRate"] <- "Verified False Rate"
names(j)[names(j) == "UnverifiedRate"] <- "Unverified Rate"
# add total to rows of the table
kable(j, caption = " Verification Results", "pandoc",format.args = list(big.mark = ","),align = c("l"))
```

Note:   
*Verified False Rate = Verified False / (Verified False + Verified True)*     
*Unverified Rate = Unverified / (Unverified + Verified False + Verified True)*


# Types of mis-reporting

```{r}
enddate_smsu2 <- format(max(datasmsu2$deliverydate),"%b %Y") #end date of smsu2.0
startdate_smsu2 <- format(min(datasmsu2$deliverydate),"%b %Y") #start date of smsu2.0
#set start and end date of smsu for putting at titles of chart
smsu2_period <- paste0("Types of mis-reporting", " ", "(" , startdate_smsu2,"-", enddate_smsu2, ")")
```

```{r}
missreport <- datasmsu2 %>% 
select(`Type of cases`,
         `ST_LBOdeliveries`,`Deliveries deleted`) %>%
   filter(`ST_LBOdeliveries` != "NA") %>% #filter out NA from 'ST-LBO deliveries'
  filter(`Type of cases` != "unverified") %>% 
group_by(`Type of cases`) %>%
  summarise(Total = sum(`Deliveries deleted`,na.rm = TRUE)) %>% 
mutate(percent = round(Total/sum(Total)*100),label = paste0(Total," ","(",percent,"%",(")")))
totalcases <- paste0("Total cases: ",sum(missreport$Total))
missreport$`Type of cases` <- reorder(missreport$`Type of cases`, missreport$Total)
ggplot(missreport,aes(x = `Type of cases`,y = Total))+ geom_bar(stat = "identity",fill="#42ffe6")+
  theme(text = element_text(family="Roboto Condensed"))+
  geom_text(aes(label=label, hjust = - 0.1,family="Roboto Condensed"),color="black",size=3)+ 
  ggtitle(smsu2_period,subtitle = totalcases)+ 
  labs(x="", y="Number of mis-reporting")+
  scale_y_continuous(breaks=seq(0,500,100),limit = c(0, 500))+
   coord_flip()+
  my_theme()
```

\newpage

# All SMSU (data from customer survey, spot check and Salesforce random)


```{r}
a <- data %>% 
select(`Total selected data`,`Type of cases`,
         `ST_LBOdeliveries`,`Deliveries deleted`) %>%
   filter(`ST_LBOdeliveries` != "NA") %>% #filter out NA from 'ST-LBO deliveries'
group_by(`ST_LBOdeliveries`) %>%
  summarise(TotalSelected = sum(`Total selected data`,na.rm = TRUE))
```

```{r}
b <- data %>% 
select(`Total selected data`,`Type of cases`,
         `ST_LBOdeliveries`,`Deliveries deleted`) %>%
   filter(`ST_LBOdeliveries` != "NA") %>% #filter out NA from 'ST-LBO deliveries'
   filter(`Type of cases` != "unverified") %>% 
group_by(`ST_LBOdeliveries`) %>%
  summarise(VerifiedFalse = sum(`Deliveries deleted`,na.rm = TRUE))
```


```{r}
c <- data %>% 
select(`Total selected data`,`Type of cases`,
         `ST_LBOdeliveries`,`Deliveries deleted`) %>%
  filter(`Type of cases` == "unverified") %>% 
   filter(`ST_LBOdeliveries` != "NA") %>% #filter out NA from 'ST-LBO deliveries'
group_by(`ST_LBOdeliveries`) %>%
  summarise(Unverified = sum(`Deliveries deleted`,na.rm = TRUE))
```


```{r, message= FALSE}
d <- right_join(a,b,by = "ST_LBOdeliveries")
```

```{r}
e <- right_join(d,c, by = "ST_LBOdeliveries")
```


```{r}
f <- data.frame(ST_LBOdeliveries = "Total" ,  TotalSelected = sum(e$TotalSelected), VerifiedFalse = sum(e$VerifiedFalse),Unverified = sum(e$Unverified))
```

```{r}
g <- rbind(e,f)
```


```{r}
h <- g %>% 
  mutate(VerifiedTrue = TotalSelected - (VerifiedFalse + Unverified))
i <- h[,c(1,2,5,3,4)] #change column position
```

```{r}
j <- i %>% 
mutate(VerifiedFalseRate = paste0(format(VerifiedFalse/(VerifiedTrue + VerifiedFalse)*100,digits = 0),"%"),
UnverifiedRate = paste0(format(Unverified/(VerifiedTrue + VerifiedFalse + Unverified)*100,digits = 0), "%"))
```


```{r}
# change column names
names(j)[names(j) == "ST_LBOdeliveries"] <- "SA/LBODeliveries"
names(j)[names(j) == "TotalSelected"] <- "Total Verification"
names(j)[names(j) == "VerifiedTrue"] <- "Verified True"
names(j)[names(j) == "VerifiedFalse"] <- "Verified False"
names(j)[names(j) == "VerifiedFalseRate"] <- "Verified False Rate"
names(j)[names(j) == "UnverifiedRate"] <- "Unverified Rate"
# add total to rows of the table
kable(j, caption = "Verification Results", format.args = list(big.mark = ","),align = c("l"))
```

Note:   
*Verified False Rate = Verified False / (Verified False + Verified True)*     
*Unverified Rate = Unverified / (Unverified + Verified False + Verified True)*

# Types of mis-reporting

```{r}
#set period for SMSU3.0
enddate <- format(max(data$deliverydate),"%b %Y") #end date
startdate <- format(min(data$deliverydate),"%b %Y") #start dete
period <- paste0("Types of mis-reporting", " ", "(" , startdate,"-", enddate, ")")
```


```{r}
missreport <- data %>% 
select(`Type of cases`,
         `ST_LBOdeliveries`,`Deliveries deleted`) %>%
   filter(`ST_LBOdeliveries` != "NA") %>% #filter out NA from 'ST-LBO deliveries'
  filter(`Type of cases` != "unverified") %>%
group_by(`Type of cases`) %>%
  summarise(Total = sum(`Deliveries deleted`,na.rm = TRUE)) %>% 
mutate(percent = round(Total/sum(Total)*100),label = paste0(Total," ","(",percent,"%",(")")))
totalcases <- paste0("Total cases: ",sum(missreport$Total))
missreport$`Type of cases` <- reorder(missreport$`Type of cases`, missreport$Total)
ggplot(missreport,aes(x = `Type of cases`,y = Total))+ geom_bar(stat = "identity",fill="#42ffe6")+
  theme(text=element_text(family="Roboto Condensed"))+
  geom_text(aes(label=label, hjust = - 0.1,family="Roboto Condensed"),color="black",size=3)+ 
  ggtitle(period,subtitle = totalcases)+ 
  labs(x="", y="Number of mis-reporting")+
  scale_y_continuous(breaks = seq(0,550,100),limit = c(0, 550))+
   coord_flip()+
  my_theme()
```


